---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# EVsales

<!-- badges: start -->
<!-- badges: end -->

The EVsales package provides tools to explore and analyze global electric vehicle (EV) sales data. It includes functions to visualize EV sales across different regions, powertrain types, and years, as well as explore predicted trends. The package is especially useful for anyone interested in understanding the rise of EV adoption globally.

## Installation

You can install the development version of EVsales from [GitHub](https://github.com/) with:

``` r
remotes::install_github("ETC5523-2024/assignment-4-packages-and-shiny-apps-xurong980623/EVsales")
```

## Example

This is a basic example showing how to explore EV sales data using the package. The following code generates a stacked bar plot of EV sales over time by region.

```{r example}
library(EVsales)
library(ggplot2)
library(tidyverse)
# Create stacked bar plot for EV sales over time
ev_sales_stacked_plot <- ev_data |>
  filter(parameter == "EV sales", Grouped_Region != "World") |>  # Corrected filter condition
  mutate(prediction_flag = ifelse(year > 2023, "Predicted", "Actual")) |>
  mutate(year = as.factor(year)) |>
  ggplot(aes(x = year, y = value, fill = Grouped_Region)) +
  geom_bar(stat = "identity", position = "stack", aes(alpha = prediction_flag)) +
  scale_fill_brewer(palette = "Set1") +
  scale_alpha_manual(values = c("Actual" = 1, "Predicted" = 0.5), guide = guide_legend(title = "Prediction")) +
  labs(title = "EV Sales Over Time by Grouped Region",
       x = "Year",
       y = "Number of EV Sales") +
  scale_y_continuous(labels = scales::comma) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
ev_sales_stacked_plot
```
This plot shows the total EV sales over time, grouped by region. Predicted values are shown with reduced opacity to differentiate them from actual sales data.

## Main Components
The EVsales package includes several key components:

- Data: Global EV sales data by region, powertrain type, and year (including predicted sales).
- Visualization Functions: Functions to create visualizations of EV sales trends, such as stacked bar charts and time series plots.
- Shiny App: An interactive Shiny app for exploring EV sales data, allowing users to filter by region, powertrain type, and year.

## How to Use the Package

- Use the provided functions to explore and visualize the EV sales dataset.
- The Shiny app can be launched using run_app(), offering an interactive interface for users to filter and analyze EV sales data.
- Data cleaning and preprocessing are handled internally to ensure a smooth user experience.

## Contributing
I welcome contributions to the EVsales package! If you find any issues or have suggestions, feel free to submit an issue or pull request on GitHub.

## License
This package is licensed under the MIT License.

## References
International Energy Agency. (2024). Global EV outlook 2024. International Energy Agency. https://www.iea.org/reports/global-ev-outlook-2024

## Visit the package documentation at:

[https://etc5523-2024.github.io/assignment-4-packages-and-shiny-apps-xurong980623/](https://etc5523-2024.github.io/assignment-4-packages-and-shiny-apps-xurong980623/)

